Out-of-Sample Comparisons of Overfit Models

### 2013-10-18 paper.tex
Move bibtex to external submodule
Add date generation to makefile
Added code to the makefile to display the date of the commit, the branch, and
the commit SHA (all automatically generated by `make ver`) in the date field
and as a running header on every page.
Update theorem and lemma numbering
Switches from Section.number to just number (at editor's request).
Prove testing result on conditional probability
This commit adds a proof of what was Corollary 1, that the conditional
probability of rejection given E_T D_T =< 0 is actually less than or
equal to alpha.  I've also changed it to be listed

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{claim}[thm]{Claim}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

@@

%% from http://blog.blubinc.net/
% Define a command for a given term. This will create a command which gives
% the long name, with a parenthesised acronym, on the first call.
% Additionally it will redefine itself to call the acronym function instead
% on subsequent executions.
%
% Takes:
%	1, command name
%	2, long name
%	3, acronym
% ie \newacronym{ols}{Ordinary Least Squares}{OLS} will define the
% command \ols

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
    Conference, and in many seminars at \textsc{ucsd}, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 \textsc{rfs} paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}
\date{October 24, 2011}

@@

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\oosA$, is asymptotically normal and centered on the expected future
performance, $t$-tests constructed from the \oos\ errors necessarily
test hypotheses about $\E_T \oosB$ and not the performance of the
pseudo-true models or the unconditional performance of the models.
This application to testing can be expressed as a corollary:
\begin{cor}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold.  Then
\begin{equation}
  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R \geq z_{\alpha} \mid \E_{T}
  \oosB \leq 0] \leq \alpha.
\end{equation}
\end{cor}

@@

\appendix
\section*{Appendix: Mathematical Details}
\setcounter{section}{1}

@@

@@

\bibliographystyle{abbrvnat}
\bibliography{AllRefs}

>>>>

\pagestyle{myheadings}
\newtheorem{thm}{Theorem}
\newtheorem{lem}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem{cor}{Corollary}
\newtheorem{asmp}{Assumption}
\newtheorem{example}{Example}
\newtheorem{defn}{Definition}

@@

\input{VERSION.tex}
\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: \texttt{gcalhoun@iastate.edu}. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 \textsc{nber}/\textsc{nsf} Time-Series
    Conference, and in many seminars at \textsc{ucsd}, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 \textsc{rfs} paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

@@

This result allows forecasters to use the \dmw\ test to conduct
inference about the models' accuracy.  Since the \oos\ average,
$\oosA$, is asymptotically normal and centered on the expected future
performance, $t$-tests constructed from the \oos\ errors necessarily
test hypotheses about $\E_T \oosB$ and not the performance of the
pseudo-true models or the unconditional performance of the models.
This application to testing can be expressed as its own theorem:
\begin{thm}\label{res:oostest}
Suppose that the conditions of Theorem \ref{res-confidence-intervals}
hold and that $\lim \Pr[\E_T \oosB \leq 0] > 0$.  Then
\begin{equation}
  \lim \Pr[P^{1/2}\oosA/\hat\sigma_R > z_{\alpha} \mid \E_T
  \oosB \leq 0] \leq \alpha.
\end{equation}
\end{thm}

@@

\appendix
\section*{Appendix: Mathematical Details}
\setcounter{section}{1}
% Change lemma style to prepend 'A'
\setcounter{lem}{0}
\renewcommand{\thelem}{A\arabic{lem}}

@@

\subsection*{Proof of Theorem \ref{res:oostest}}
By Lemma~\ref{res-convergence}, we know that
\begin{equation*}
  \Pr[\E_R \oosA \leq 0] - \Pr[\E_T \oosB \leq 0] \to 0
\end{equation*}
and
\begin{equation*}
  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } \E_R \oosA \leq 0]
  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and } 
  \E_T \oosB \leq 0] \to 0.
\end{equation*}
For large enough $T$, both $\Pr[\E_R \oosA \leq 0]$ and $\Pr[\E_T
\oosB \leq 0]$ are positive, so
\begin{equation*}
  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
  \mid \E_R \oosA \leq 0] = 
  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
    \E_R \oosA \leq 0]}{\Pr[\E_R \oosA \leq 0]}
\end{equation*}
and
\begin{equation*}
  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
  \mid \E_T \oosB \leq 0] = 
  \frac{\Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \text{ and }
    \E_T \oosB \leq 0]}{\Pr[\E_T \oosB \leq 0]}
\end{equation*}
almost surely and consequently
\begin{equation*}
  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
  \mid \E_T \oosB \leq 0]
  - \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha
  \mid \E_R \oosA \leq 0] \to^p 0.
\end{equation*}
Finally,
\begin{align*}
  \Pr[P^{1/2} \oosA / \hat\sigma > z_\alpha \mid \E_R \oosA \leq 0]
  &\leq \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
  \mid \E_R \oosA \leq 0] \\
  &= \E( \Pr[P^{1/2} (\oosA - \E_R \oosA) / \hat\sigma > z_\alpha 
  \mid \mathcal{F}_R] \mid \E_R \oosA \leq 0) \\
  &= \E(\alpha \mid \E_R \oosA \leq 0) \\
  &= \alpha
\end{align*}
where the second equality holds by Lemma~\ref{res-mixingale} and
Theorem~\ref{res-variance-estimator}, completing the proof.
\qed

@@

\bibliographystyle{abbrvnat}
\bibliography{texextra/AllRefs}
